\textit{Red Oak}\\ Proactive Controller Generation for Algorithmic Policy

### 2015-05-11 draft.tex
..

We introduce a high-level SDN library that can be embedded into existing languages.
Our library exposes an API that allows programmers to directly express behavioral intent, 
while leaving the performance details to the library's optimization algorithms.
Our library supports basic tests on packet fields as well as a simple mutable table
data structure for storing global network information (e.g., firewall ACL, MAC learning table).
Finally, to ensure adequate performance, 
we statically analyze the programmer's policy by pushing symbolic packets through the policy 
and observing the resulting packet forwarding decision.
\end{abstract}

@@

One of the major outcomes of the Software Defined Networking (SDN) movement has been a unified, open interface to the switch hardware. This has, in turn, enabled new opportunities for network programmability. The typical model for SDN involves a centralized controller or distributed set of controllers programming switches dynamically to implement the desired control functionality.
However, the questions remains as to how best to write programs for SDNs.

@@

Ultimately, the performance requirements of networks dictate that the centralized controller(s) can not handle most traffic since redirecting packets to be handled by the controller incurs orders of magnitude increased latency compared to those being handled by switches. For this reason, compiler technologies for network programming languages must be able to push much of the control plane functionality into the data plane switches themselves.

For Maple, the authors show how to optimize the controller so that packets are handled without having to run the function on them. Maple does so by providing a packet API capturing each access to packet fields, and memoizing the results of the function for subsequent packets sharing the accessed fields' values. Unfortunately, there are a number of limitations to this approach:

>>>>

We developed a high-level SDN library that can be embedded into existing languages.
Our library exposes an API that allows programmers to directly express behavioral intent, 
while leaving the performance details to the library's optimization algorithms.
Our library supports basic tests on packet fields as well as a simple mutable table
data structure for storing global network information (e.g., firewall ACL, MAC learning table).
Finally, to ensure adequate performance, 
we statically analyze the programmer's policy by pushing symbolic packets through the policy 
and observing the resulting packet forwarding decision.
\end{abstract}

@@

One of the major outcomes of the Software Defined Networking (SDN) movement has been a unified, open interface to the switch hardware. This has, in turn, enabled new opportunities for network programmability. The typical model for SDN involves a centralized controller or distributed set of controllers programming switches dynamically to implement the desired control functionality.
However, the question remains as to how best to write programs for SDNs.

@@

Ultimately, the performance requirements of networks dictate that the centralized controller(s) should not handle most traffic since redirecting packets to be handled by the controller incurs orders of magnitude increased latency compared to those being handled by switches. For this reason, compiler technologies for network programming languages must be able to push much of the control plane functionality into the data plane switches themselves.

In Maple \cite{Maple}, the authors show how to optimize the controller to reduce the number of packets are handled by running the function on them. Maple does so by providing a packet API capturing each access to packet fields, and memoizing the results of the function for subsequent packets sharing the accessed fields' values. Unfortunately, there are a number of limitations to this approach:
